null_model

### 2021-03-24 analysis/ts_null_model.Rmd
Clean up and clarifications

```{r}
library(tidyverse)
library(biodivTS)
library(FD)
library(furrr)

pins::board_register_github(repo = "karinorman/biodivTS", branch = "master")
```

@@

Get dataframe of samples for each plot and corresponding species and trait matrices
```{r}
biotime_traits <- pins::pin_get("biotime-traits", board = "github")

>>>>

```{r}
library(tidyverse)
#library(biodivTS)
library(FD)
library(furrr)

pins::board_register_github(repo = "karinorman/biodivTS_data", branch = "master")
```

@@

Get dataframe of samples for each plot and corresponding species and trait matrices
```{r}
biotime_traits <- pins::pin_get("bt-traitfiltered", board = "github")
